\chapter{Experiments}
In this section, we present an overview of the models and experiments performed in our study. We evaluated four models: Random Forest (RF), Adversarial Joint-Learning Recurrent Neural Network (AJ-RNN), Temporal Convolutional Neural Network (TempCNN), and Lightweight Temporal Self-Attention Encoder (L-TAE).

For each model, we provide a description of its architecture.
We also compare the original authors' findings on the hyperparameters configurations with our own observations.
In addition, we discuss any adaptations or modifications made to the original model architecture to better fit our specific problem.

Our experiments were conducted on two datasets: one with pre-imputed missing values and the other without imputation. 
We compare the performance of each model on both datasets and examine any differences in their performance.

\input{contents/experiments/rf}
\pagebreak
\input{contents/experiments/tempcnn}
\pagebreak
\input{contents/experiments/ajrnn}
\pagebreak
\input{contents/experiments/ltae}
\pagebreak

\section{Comparing results}

In this section, we compare the performance of the different models on both the imputed and non-imputed datasets.

\begin{table}[H]
  \centering
    \begin{tabular}{lr}
    Model                       & Overall Accuracy             \\[0.2cm] 
    \hline \\[-0.2cm]
    RF            & $91.03 \pm 0.42$\\
    Light AJ-RNN  & $87.29 \pm 1.08$\\
    TempCNN       & $93.74 \pm 0.03$\\
    L-TAE         & $93.58 \pm 1.29$
    \end{tabular}
  \caption{Overall accuracy of the best models with pre imputed missing values}
  \label{tab:ALLresultsImputed} 
\end{table}

\begin{table}[H]
  \centering
    \begin{tabular}{lr}
    Model                       & Overall Accuracy             \\[0.2cm] 
    \hline \\[-0.2cm]
    RF      & $89.72 \pm 0.84$\\
    AJ-RNN  & $86.07 \pm 1.58$\\
    TempCNN & $92.57 \pm 0.84$\\
    L-TAE   & $93.65 \pm 1.30$
    \end{tabular}
  \caption{Overall accuracy of the best models without imputation of missing values} 
  \label{tab:ALLresultsNoImputed}
\end{table}

Overall, our experiments show that TempCNN and L-TAE outperformed the other models on both datasets.
Specifically, L-TAE achieved an accuracy of 93.58\% and 93.65\% on the imputed and non-imputed datasets, respectively, 
while TempCNN achieved an accuracy of 93.74\% and 92.57\%. RF and AJ-RNN both achieved lower accuracies. 
These results suggest that deep learning models such as TempCNN and L-TAE may be more suitable for modeling satellite image time series data.

\subsection{Imputation of missing values}

The inclusion of missing data can often be a challenge in machine learning tasks, as missing values can have a significant impact on the performance of the model.
In the first scenario, we addressed this issue by imputing the missing values prior to training the models. 
This allowed us to utilize all available data in the training process, leading to potentially improved performance.

In the second scenario, we did not impute the missing values, which meant that the training process was carried out using only the available non-missing data.
This scenario can be particularly useful in cases where imputation may introduce bias or distort the underlying patterns in the data.

Overall, the results reported in Tables \ref{tab:ALLresultsImputed} and \ref{tab:ALLresultsNoImputed} demonstrate that the inclusion of missing data through imputation did not significantly impact the performance of the models.